\documentclass[11pt,a4paper]{article}

\usepackage[margin=1in]{geometry}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[hidelinks,colorlinks=true,linkcolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[strings]{underscore}
\usepackage{xurl}
\newcommand{\doi}[1]{\href{https://doi.org/#1}{\nolinkurl{#1}}}

\definecolor{codebg}{RGB}{245,245,248}
\definecolor{rule}{RGB}{40,60,120}
\definecolor{v2col}{RGB}{150,75,0}
\definecolor{v3col}{RGB}{0,90,40}
\definecolor{okgreen}{RGB}{0,120,50}
\definecolor{warnamber}{RGB}{170,110,0}

\lstdefinestyle{sh}{basicstyle=\ttfamily\small,backgroundcolor=\color{codebg},frame=single,
  rulecolor=\color{rule!30},breaklines=true,columns=fullflexible,keepspaces=true,
  showstringspaces=false,xleftmargin=8pt,aboveskip=6pt,belowskip=6pt}
\lstset{style=sh}
\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\yes}{\textcolor{okgreen}{\textbf{yes}}}
\newcommand{\no}{\textcolor{warnamber}{no}}

\pagestyle{fancy}\fancyhf{}
\lhead{\small HEBCPF Solver Suite}\rhead{\small Overview \& Selection Guide}
\cfoot{\small\thepage}\renewcommand{\headrulewidth}{0.4pt}

\setlength{\parskip}{4pt}\setlength{\parindent}{0pt}

% ---- looser line breaking so long code tokens/lists do not overrun the margin ----
\tolerance=3000
\emergencystretch=3em

\begin{document}

% ===================== TITLE =====================
\begin{titlepage}
\centering
\vspace*{2.0cm}
{\color{rule}\rule{\textwidth}{1.2pt}}\\[8pt]
{\Huge\bfseries HEBCPF Solver Suite}\\[10pt]
{\LARGE Overview and Version Selection Guide}\\[10pt]
{\color{rule}\rule{\textwidth}{1.2pt}}\\[16pt]
{\large\itshape Finding \emph{all} real-valued solutions of the AC power-flow equations}\\[4pt]
{\large\itshape Ellipsoidal Formulation + Holomorphic Embedding + Pad\'e + Numerical Continuation}\\[26pt]

{\large This guide compares the \textbf{six} packaged releases and helps you pick one.}\\[18pt]

{\small
\begin{tabular}{@{}ll@{}}
\toprule
Release folder & Orientation\\
\midrule
\code{HEBCPF_MEX_v4_20260714}    & Performance-optimized compiled build, Windows x64\\
\code{HEBCPF_matlab_v4_20260714} & Performance-optimized portable build, any OS\\
\code{HEBCPF_MEX_v3.20260712}    & Robustness-oriented, compiled --- hardened config, Windows x64\\
\code{HEBCPF_matlab_v3.20260712} & Robustness-oriented, portable --- hardened config, any OS\\
\code{HEBCPF_MEX_v2.20260712}    & Efficiency-oriented, compiled --- legacy-fast config, Windows x64\\
\code{HEBCPF_matlab_v2.20260712} & Efficiency-oriented, portable --- legacy-fast config, any OS\\
\bottomrule
\end{tabular}
}

\vfill
{\small Solver lines are v4.20260714, v3.202606, and v2.202607; this package release is dated 2026.07.14.}\\[6pt]
{\small Each release also ships its own detailed \code{HEBCPF_User_Guide.pdf}. When you
publish results, cite the HEBC paper (Section~\ref{sec:cite}).}\\[6pt]
{\small Package release: July 14, 2026}
\end{titlepage}

\tableofcontents
\newpage

% ===================== 1 =====================
\section{What all six releases have in common}
Every release implements the \textbf{same method} --- the Holomorphic Embedding Based
Continuation (HEBC) all-solutions power-flow tracer --- and returns the same solution set
on the completed benchmark cases. They also share:
\begin{itemize}[leftmargin=1.4em]
  \item the same dependency: MATLAB + MATPOWER (\code{runpf} for the initial point
        and \code{makeYbus} for the bus-admittance matrix);
  \item the same three execution frameworks --- serial (\code{run_batch.m}),
        \code{parfor} (\code{run_batch_par.m}), and \code{parfeval}
        (\code{run_batch_parfeval.m}, recommended for large cases);
  \item the same single-case programmatic harness \code{run_merged_case};
  \item identical bundled test systems and the same published solution-count references
        (Table~\ref{tab:counts});
  \item the same bordered-Newton formulation on the numerical hot path. MEX releases use the
        KLU symbolic-once refactorisation, which keeps the \emph{exact} Jacobian and scales
        to ${\sim}7.5\times$ on \code{case118}. MATLAB v2/v3 can use a compatible
        \code{klurf} MEX; MATLAB v4 deliberately uses MATLAB built-ins only.
\end{itemize}
On completed benchmark cases, \textbf{the choice between releases is about
\emph{robustness}, \emph{speed}, and \emph{platform} --- never about correctness of the
answer on well-behaved systems.}

\begin{table}[h]\centering\small
\caption{Reference number of real solutions (antipodal pairs collapsed). Values through
\code{case57} are completed benchmarks; \code{case118} is a partial enumeration, not a
claimed total.}\label{tab:counts}
\begin{tabular}{@{}lr@{\qquad}lr@{}}
\toprule
System & \# sol. & System & \# sol.\\
\midrule
\code{case3}      & 6  & \code{case14mod}         & 30\\
\code{case4gs}    & 6  & \code{case33bw}          & 16\\
\code{case4BB0}   & 14 & \code{case39}            & 176\\
\code{case4BBc}   & 12 & \code{case30}/\code{case_ieee30} & 472\\
\code{case5loop}  & 10 & \code{case57mod}         & 606\\
\code{case5Salam} & 10 & \code{case57}            & 1322\\
\code{case6ww}    & 6  & \code{case118}           & $>1.5\times10^{6}$ (partial)\\
\code{case7Salam} & 4  & &\\
\code{case9}/\code{case9Q} & 8 & &\\
\bottomrule
\end{tabular}
\end{table}

\section{Changes in package release 2026.07.14}
Compared with the publicly released \code{HEBCPF} baseline folders (solver lines
\code{v2.202607} and \code{v3.202606}), this package keeps the HEBC formulation and the
v2/v3 numerical configurations unchanged. Package 2026.07.12 added:
\begin{itemize}[leftmargin=1.4em]
  \item the bordered Newton corrector now has a sparse-core Schur-complement path with
        SuiteSparse/KLU symbolic-once refactorisation. The MEX releases include
        \code{klurf.mexw64}; the top-level \code{klurf/} folder provides the source and
        build helper for other MEX platforms or for the optional-KLU MATLAB v2/v3 releases;
  \item keyed bucket lookup accelerates repeated-solution collection in the serial,
        \code{parfor}, and \code{parfeval} collectors;
  \item geometric \code{Zsave} growth avoids repeated full-array copies while collecting
        newly discovered solutions;
  \item the Jacobian cache has a lower-overhead hot path after its per-trace initialisation.
\end{itemize}

Package 2026.07.14 adds the compiled \code{HEBCPF_MEX_v4_20260714} release. Relative to
MEX v3, v4 uses a global per-equation \code{parfeval} queue, caches the sparse LU ordering
of the holomorphic matrix, reuses sparse holomorphic-assembly invariants, and evaluates
Pad\'e polynomials with matrix-vector products instead of replicated temporary matrices.
The prior barrier scheduler remains available as \code{runVBook_hybrid_parfeval_barrier.m}
for controlled comparisons.
The same release also adds \code{HEBCPF_matlab_v4_20260714}: the portable counterpart
retains those v4 scheduling and holomorphic-kernel optimizations while using MATLAB built-in
linear algebra exclusively in its correctors.

% ===================== 2 =====================
\section{The two axes of choice}
The v2/v3 releases are the combinations of two independent choices. MEX v4 and pure MATLAB
v4 are performance-optimized successors to their v3 counterparts and keep the v3 numerical
configuration.

\subsection*{Axis 1 --- \textcolor{v2col}{v2 (legacy-fast)} vs.\ \textcolor{v3col}{v3 (validated / robust)}}
This is the important one. \textbf{v2} is the fast legacy configuration; \textbf{v3} is the
robustness-hardened configuration developed and validated to eliminate the numerical
failures (wrong-branch drift, non-closing loops) that the legacy settings can hit on sharp
or fold-dense curves.

\begin{center}\footnotesize
\renewcommand{\arraystretch}{1.25}
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.21\textwidth}
                   >{\raggedright\arraybackslash}p{0.34\textwidth}
                   >{\raggedright\arraybackslash}p{0.36\textwidth}@{}}
\toprule
\textbf{Aspect} & \textcolor{v2col}{\textbf{v2 --- legacy-fast}} & \textcolor{v3col}{\textbf{v3 --- validated / robust}}\\
\midrule
Settings location & inlined in \code{hybrid_traceloops} & centralised in \code{solver_params.m}\\
Turning-point slope limit (\code{slope_max}) & \code{4e5} & \code{4e5} --- shared release default\\
Hand-back hysteresis (\code{handback}) & \code{0.1} & \code{0.5} --- clears the fold first\\
Fold initial-step cap (\code{init_cap_k}) & \emph{none} & \code{1500}\\
Adaptive step cap (\code{max_adapt}) & \emph{none} & \code{true} --- secant-slope driven\\
Pad\'e pole estimate & consensus (\code{'fixed'}/\code{'random'} toggle) & consensus, fixed bus set \code{2:6}\\
Speed & \textcolor{v2col}{faster ($\approx$10--20\% in parfeval)} & modestly slower in parfeval\\
Robustness & may stall (500-cap) on hard curves & \textcolor{v3col}{hardened by fold-step and hand-back safeguards}\\
\bottomrule
\end{tabular}
}
\end{center}

Both give the same counts on well-behaved systems. The difference shows up on
\emph{hard} curves (sharp thin-sliver folds, fold-dense loops --- e.g.\ some case118,
case30 and case57mod curves): v2 may burn its alternation cap on a wrong/non-closing branch
(costing time; the solution is still found by a neighbouring trace so the \emph{count}
stays exact), whereas v3 keeps the trace on the true branch by adding the three safeguards
below.

\subsection*{The extra conditions and criteria in v3 (absent in v2)}
Every safeguard acts \emph{only near singular points} (turning points / folds) and during
the hand-off between the holomorphic and continuation routines. With the shared
\code{slope_max = 4e5} default, the three
additional v3 safeguards are:

\begin{enumerate}[leftmargin=1.5em]
  \item \textbf{Fold-proximity initial-step cap} (\code{init_cap_k = 1500}). When the
        holomorphic routine hands over to the continuation near a fold, the holomorphic arc
        that just collapsed, \code{holo_arc}, is a proxy for how close the fold is. v3 caps
        the \emph{first} continuation step to \code{astep <= init_cap_k * holo_arc / sstep}:
        a near-fold hand-off (small \code{holo_arc}) forces a small, careful first step,
        while a smooth hand-off (large \code{holo_arc}) is left at full step. v2 has no such
        cap, so its first step can be large enough to jump the fold onto the adjacent (wrong)
        branch.
  \item \textbf{Secant-slope adaptive per-step cap} (\code{max_adapt = true}). At every
        continuation step v3 measures the two-point secant slope
        $s_k=\lVert\Delta\text{state}\rVert/\lvert\Delta\alpha\rvert$ and caps the next step
        by how fast that slope is changing:
        \code{astep <= maximumstep * min(s_prev/s, 1)}. As the curve steepens toward a fold
        ($s$ rising) the ceiling tightens automatically; once the fold is passed it relaxes
        back to the full \code{maximumstep}. v2 has no curvature-aware per-step cap.
  \item \textbf{Larger hand-back hysteresis} (\code{handback}: \code{0.5} in v3 vs \code{0.1}
        in v2). Before handing back, the continuation must travel
        \code{handback}\,$\times$\,\code{aal_min} \emph{past} the homotopy-parameter
        ($\alpha$) reversal, so the near-singular zone is fully cleared. v3 clears five times
        as much of that zone as v2, which is what stops the curve being pulled back onto an
        adjacent branch on the holomorphic restart.
\end{enumerate}
Because these fire only near singularities, v3's overall speed cost is small
(Section~\ref{sec:timing}) while its robustness gain on hard curves is decisive.

\subsection*{Axis 2 --- MEX vs.\ MATLAB (pure)}
\begin{center}\small
\renewcommand{\arraystretch}{1.25}
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.235\textwidth}
                   >{\raggedright\arraybackslash}p{0.335\textwidth}
                   >{\raggedright\arraybackslash}p{0.345\textwidth}@{}}
\toprule
\textbf{Aspect} & \textbf{MEX build} & \textbf{MATLAB (pure) build}\\
\midrule
Hot path      & 2 compiled MEX (\code{Pade_Apprxmt}, \code{holomorphic_cont_tri}) & plain \code{.m} only\\
Bordered solve & KLU symbolic-once refactor --- \code{klurf.mexw64} shipped, on by default & MATLAB v4: built-in \code{\textbackslash}; MATLAB v3/v2: built-in or compatible \code{klurf}\\
Serial speed  & \textbf{$\approx 2\times$ faster} & baseline\\
Platform      & Windows 64-bit (shipped binaries) & \textbf{any} --- Windows / Linux / macOS\\
Compiler      & MATLAB Coder, only to rebuild or port & none, ever\\
Extra files   & \code{*.mexw64}, \code{build_mex.m}, \code{examples.mat} & \emph{none}\\
Numerical result & \multicolumn{2}{c}{\emph{identical} (verified to $\sim 10^{-13}$)}\\
\bottomrule
\end{tabular}
\end{center}
The MEX and MATLAB builds of the \emph{same} version are designed to return interchangeable,
bit-comparable solution sets; MEX is primarily a speed/platform choice. MATLAB v4 deliberately
keeps its corrector path pure MATLAB and never calls \code{klurf}.

% ===================== 3 =====================
\section{Choosing a release}
All six releases are intended to return the same solution set. \textbf{When no specific
compatibility, legacy-reproduction, or platform preference applies, choose v4 as the default
solver}: choose \textbf{MEX v4} on supported Windows x64 installations, and choose
\textbf{MATLAB v4} on other platforms or when a pure-MATLAB implementation is preferred.
The v3 and v2 releases remain available as established and legacy reference configurations.

\begin{description}[leftmargin=0em,style=nextline]
\item[\textbf{MEX v4}] Choose this on supported Windows x64 installations when wall-clock
      performance is the priority. It retains the v3 hardened numerical configuration, adds
      the global \code{parfeval} work queue and cached hot-path kernels, and has reported
      \code{parfeval} speed-ups of 1.21--1.59$\times$ over MEX v3 on six cases
      (Section~\ref{sec:timing}).
\item[\textbf{MATLAB v4}] Choose this when portability and readable \code{.m}-only code
      matter, while still wanting the v4 scheduling and cached numerical kernels. Its
      correctors use only MATLAB built-ins; no MEX binary, compiler, KLU, or \code{klurf}
      dependency is required.
\item[\textcolor{v3col}{\textbf{MEX v3 / MATLAB v3}}] Choose an established hardened v3
      release when reproducing earlier v3 work or when the v4 changes are not desired. MEX v3
      is the compiled Windows x64 option; MATLAB v3 is the portable option.
\item[\textcolor{v2col}{\textbf{MEX v2 / MATLAB v2}}] Choose only for legacy reproduction or
      for well-behaved cases where the historical v2 configuration is specifically wanted.
      It can be faster under historical \code{parfeval} measurements, but it lacks v3/v4's
      fold-hardening safeguards.
\end{description}

% ===================== 4 =====================
\section{Feature matrix}
\begin{center}\footnotesize
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lcccccc@{}}
\toprule
& \code{MEX_v4} & \code{matlab_v4} & \code{MEX_v3} & \code{matlab_v3} & \code{MEX_v2} & \code{matlab_v2}\\
\midrule
Robustness-hardened config (v3)      & \yes & \yes & \yes & \yes & \no  & \no\\
\code{solver_params.m} single-source & \yes & \yes & \yes & \yes & \no  & \no\\
Fold-proximity step caps             & \yes & \yes & \yes & \yes & \no  & \no\\
Consensus Pad\'e poles               & \yes & \yes & \yes & \yes & \yes & \yes\\
\code{'fixed'}/\code{'random'} pole toggle & \no & \no & \no & \no & \yes & \yes\\
Global \code{parfeval} work queue     & \yes & \yes & \no & \no & \no & \no\\
Cached holomorphic sparse-LU ordering & \yes & \yes & \no & \no & \no & \no\\
Reused sparse holomorphic assembly invariants & \yes & \yes & \no & \no & \no & \no\\
Allocation-free Pad\'e evaluation     & \yes & \yes & \no & \no & \no & \no\\
Corrector uses MATLAB built-ins only  & \no  & \yes & \no & \yes & \no & \yes\\
Compiled MEX ($\approx 2\times$ serial) & \yes & \no & \yes & \no & \yes & \no\\
Cross-platform (no compiler)         & \no  & \yes & \no  & \yes & \no  & \yes\\
Serial / \code{parfor} / \code{parfeval} & \yes & \yes & \yes & \yes & \yes & \yes\\
Identical solution counts            & \yes & \yes & \yes & \yes & \yes & \yes\\
\bottomrule
\end{tabular}
}
\end{center}

% ===================== 5 =====================
\section{Numerical test bed and timing comparison}\label{sec:timing}

\subsection{Test bed}\label{sec:testbed}
All timings in this section were measured on a single dedicated workstation, one MATLAB
process at a time (no concurrent jobs), to minimise interference:
\begin{center}\small
\begin{tabular}{@{}ll@{}}
\toprule
Component & Specification\\
\midrule
CPU & Intel Core i9-13900K --- 24 cores / 32 threads (8 performance + 16 efficiency cores)\\
RAM & 128\,GB\\
Operating system & Microsoft Windows 11 Pro, version 22H2 (build 22621)\\
MATLAB & R2022a (9.12.0), \code{maxNumCompThreads} = 24\\
Parallel pool & \code{local} profile, 23 workers\\
Initial solve & MATPOWER 7.1 \code{runpf} (for the starting operating point)\\
\bottomrule
\end{tabular}
\end{center}
For the completed cases listed in the timing tables, solution \emph{counts} were verified
identical across releases; only wall-clock time differs. \textbf{Serial} figures
are a single timed run per case; \textbf{\code{parfeval}} figures are the \emph{mean of
three back-to-back trials} on a warmed pool (the one-time $\sim$45\,s pool start-up is
excluded). All times are the trace wall-clock returned by \code{run_merged_case}.

These figures are a \emph{historical dense-bordered-solve baseline}; they are retained for
version selection and are not an end-to-end timing claim for package 2026.07.14. The current
MEX releases ship the \textbf{KLU symbolic-once refactor}. MATLAB v3 can use a compatible
\code{klurf} MEX, whereas MATLAB v4 deliberately keeps its correctors on MATLAB built-ins.
KLU further reduces time on larger systems --- a wash below \code{case30}, but up to
${\sim}7.5\times$ on \code{case118}. See each User Guide for the applicable linear-solver
details.

\subsection{All reported MEX v4 \code{parfeval} timings}
MEX v4 was developed against MEX v3 on the same 23-worker local-pool setup. The following
development-time values are means of two runs, excluding pool start-up; they are included as
a reference and were \textbf{not re-executed during this package-preparation pass}. The
development record reports order-insensitive matching of the same solution sets through
\code{case57}.
\begin{center}\small
\begin{tabular}{@{}lrrr@{}}
\toprule
System & MEX v3 (s) & MEX v4 (s) & v3/v4 speed-up\\
\midrule
\code{case9} & 1.61 & 1.33 & 1.21$\times$\\
\code{case14mod} & 5.57 & 3.91 & 1.42$\times$\\
\code{case33bw} & 8.22 & 5.66 & 1.45$\times$\\
\code{case39} & 49.93 & 38.64 & 1.29$\times$\\
\code{case30} & 101.81 & 63.96 & 1.59$\times$\\
\code{case57mod} & 236.43 & 175.70 & 1.35$\times$\\
\bottomrule
\end{tabular}
\end{center}

\subsection{MATLAB v4 validation results}
MATLAB v4 has a documented correctness-validation record, rather than a corresponding
wall-clock timing series. The following are all recorded MATLAB v4 results from
2026-07-14; the set errors compare MATLAB v4 with MEX v4 in both matching directions.
\begin{center}\small
\begin{tabular}{@{}ll@{}}
\toprule
Run or comparison & Recorded result\\
\midrule
\code{case3}, serial & 6 solutions; maximum residual \code{1.69e-14}\\
\code{case3}, MATLAB v4 vs.\ MEX v4 & 6 vs.\ 6; bidirectional set error \code{2.42e-14} L1\\
\code{case9}, serial & 8 solutions; maximum residual \code{7.39e-13}\\
\code{case9}, MATLAB v4 vs.\ MEX v4 & 8 vs.\ 8; bidirectional set error \code{2.89e-12} L1\\
\code{case14mod}, serial & 30 solutions; maximum residual \code{9.25e-13}\\
\code{case14mod}, MATLAB v4 vs.\ MEX v4 & 30 vs.\ 30; bidirectional set error \code{2.49e-12} L1\\
\code{case3}, \code{parfeval} & pool started; 6 solutions; maximum residual \code{2.35e-14}\\
\bottomrule
\end{tabular}
\end{center}
No MATLAB v4 wall-clock series was supplied, so this overview makes no numerical timing
claim for MATLAB v4 versus MATLAB v3, MEX v4, or the v2 releases. Its v4 queue and cached
kernels are an implementation improvement; its all-MATLAB corrector is a deliberate
portability trade-off rather than a measured speed conclusion.

\subsection{Serial timings --- single trial (seconds)}
\begin{center}\small
\begin{tabular}{@{}lrrrrr@{}}
\toprule
System & \# sol. & \code{MEX_v2} & \code{MEX_v3} & \code{matlab_v2} & \code{matlab_v3}\\
\midrule
\code{case9}     & 8   & 1.4  & 1.5  & 2.0  & 2.4\\
\code{case14mod} & 30  & 8.2  & 9.4  & 14.0 & 15.9\\
\code{case33bw}  & 16  & 19.9 & 25.1 & 33.7 & 42.4\\
\code{case39}    & 176 & 513  & 440  & 558  & 627\\
\code{case30}    & 472 & 946  & 527  & 793  & 897\\
\code{case57mod} & 606 & 4502 & 2737 & 3548 & 3984\\
\bottomrule
\end{tabular}
\end{center}

\subsection{\code{parfeval} timings --- mean of 3 trials (seconds)}
\begin{center}\small
\begin{tabular}{@{}lrrrrr@{}}
\toprule
System & \# sol. & \code{MEX_v2} & \code{MEX_v3} & \code{matlab_v2} & \code{matlab_v3}\\
\midrule
\code{case9}     & 8   & 0.6   & 0.7   & 0.9   & 1.0\\
\code{case14mod} & 30  & 3.5   & 3.8   & 5.8   & 6.0\\
\code{case33bw}  & 16  & 5.6   & 8.4   & 10.3  & 12.7\\
\code{case39}    & 176 & 49.3  & 58.7  & 71.1  & 75.2\\
\code{case30}    & 472 & 90.6  & 104.3 & 169.4 & 162.3\\
\code{case57mod} & 606 & 268.7 & 304.9 & 408.3 & 421.1\\
\bottomrule
\end{tabular}
\end{center}

\textbf{How to read these tables --- four findings.}
\begin{enumerate}[leftmargin=1.5em]
  \item \textbf{MEX v4 improves on MEX v3 in every recorded v4 timing.} Across all six
        reported \code{parfeval} cases, MEX v4 is 1.21--1.59$\times$ faster than MEX v3.
        This is the directly comparable v4 performance result: both columns use the same
        development-time two-run, 23-worker protocol.
  \item \textbf{Use \code{parfeval} for anything large.} On this 24-core machine parfeval is
        \textbf{5--17$\times$} faster than serial on the big cases (e.g.\ \code{MEX_v3}
        case57mod: 2737\,s serial $\to$ 305\,s parfeval). Serial is best reserved for small
        systems, reproducibility, and debugging.
  \item \textbf{The v2-vs-v3 winner depends on the mode.} Under \code{parfeval} the legacy
        \emph{v2} is $\approx$10--20\% faster than the hardened \emph{v3}: its lighter
        per-step config wins and its occasional wrong-branch stalls are absorbed across 23
        workers. In \emph{serial} this \emph{reverses} on the large MEX cases ---
        \code{MEX_v3} beats \code{MEX_v2} by up to \textbf{1.6$\times$} (case57mod 2737\,s vs
        4502\,s) --- because v2's legacy settings hit wrong-branch stalls that each burn the
        500-step cap, and in serial there is no other worker to hide that cost. \emph{So
        v2's speed edge exists only in parallel; for serial runs on large or hard systems v3
        is both safer and faster.} (v2's large-case serial times even differ between the MEX
        and pure-MATLAB builds because tiny floating-point differences change which curves
        stall --- a further argument for v3's predictability.)
  \item \textbf{MEX vs pure-MATLAB.} Under \code{parfeval} MEX is $\approx$1.2--1.6$\times$
        faster than the pure-MATLAB build of the same version (v3 case57mod 305\,s vs
        421\,s). This is smaller than the $\approx 2\times$ MEX advantage seen in
        \emph{serial}, because parfeval already spreads the work across workers so per-trace
        speed matters less. This historical observation applies to v2/v3 only; MATLAB v4 has
        validation results above, but no recorded timing series.
\end{enumerate}
The historical v2/v3 tables and the MEX v3/v4 table use different benchmark passes and trial
counts, so they should not be combined into a direct six-release ranking. Times carry the
usual parallel run-to-run variance ($\pm$10--15\%); read each internally consistent table as
a ratio guide, not as an absolute cross-table ranking.

% ===================== 6 =====================
\section{Where to go next}
Each release folder contains its own \code{HEBCPF_User_Guide.pdf} with installation,
quick-start, full parameter reference, the \code{parfor}-vs-\code{parfeval} explanation,
and troubleshooting specific to that build. Start there once you have picked a release from
this guide.

\section{License and third-party notices}
HEBCPF is distributed under the BSD 3-Clause License; see the top-level \code{LICENSE}
file. The suite depends on MATPOWER at runtime and calls MATPOWER functions including
\code{runpf}, \code{makeYbus}, \code{idx_bus}, and \code{idx_brch}. Some bundled
\code{caseXXX.m} files are copied from, derived from, or modified from MATPOWER and other
public test-system sources. Preserve per-file attribution notices when redistributing
modified versions, and see the top-level \code{NOTICE} file for third-party attribution
details.

The optional KLU acceleration on the bordered-solve hot path links \textbf{SuiteSparse/KLU}
(Timothy A.~Davis), distributed under the GNU LGPL-2.1-or-later license. The \code{klurf}
MEX source and a cross-platform build script are provided in the top-level \code{klurf/}
folder; see \code{klurf/README_KLURF.md} and the SuiteSparse license terms.

\section{Citing this solver}\label{sec:cite}
If you use results from any release, please cite the HEBC paper:
\begin{quote}\small
D.\ Wu and B.\ Wang, ``Holomorphic Embedding Based Continuation Method for Identifying
Multiple Power Flow Solutions,'' \emph{IEEE Access}, vol.~7, pp.~86843--86853, 2019.
doi:\,\doi{10.1109/ACCESS.2019.2925384}.
\end{quote}
For citing the software package itself, see the top-level \code{CITATION.cff} file.
The foundational and related works (elliptical branch tracing, Wu's 2017 UW--Madison thesis,
the ACOPF extension, the voltage-stability-margin application, and the IEEE Dataport
solution-set collection) are listed in each release's user guide.

\vfill
\begin{center}\small\itshape
HEBCPF Solver Suite --- Overview \& Selection Guide. Redistribute alongside the releases.
\end{center}

\end{document}
